### 2023-02-21 intro.qmd
update

::: {.blackbox data-latex=""}
::: {.center data-latex=""}
BCP and blue carbon
:::

@@

Estimates of global carbon export range between 5 and 12 Pg C year$^{-1}$ [@Laws2000-XX; @Dunne2007-mi; @Henson2011-mt; @Siegel2014-wg; @DeVries2017-wu; @Nowicki2022-no] with only 0.02-0.4 Pg C year$^{-1}$ reaching the sediment [@Dunne2007-mi; @Hayes2021-gg; @Nowicki2022-no] where carbon will be sequestered for millions of years. Almost all of the exported organic carbon will therefore be remineralized and sequestered away from the atmosphere on time scales ranging from months to millennia. [@Siegel2022-wd].

@@

The most well known pump is the gravitational carbon pump (BGP). It consists in the gravitational settling (i.e. sinking) of POC[^intro-3] to the deep ocean and it is the main contributor (60-70%) of the export flux [@Boyd2019-ez; @Nowicki2022-no]. Historically, the downward POC flux was directly measured using sediment traps [@Martin1987-um; @Honjo2008-kn] and indirectly measured using thorium-234 ($^{234}Th$) deficits as a POC flux proxy [e.g. @Buesseler2006-og]. More recently, the advent of underwater cameras such as the Underwater Vision Profiler 5 (UVP5) [@Picheral2010-to] allowed the direct measurement of particle size distributions (PSD) that could then be converted to carbon fluxes [e.g. @Guidi2008-vp].

>>>>

::: {.blackbox data-latex=""}
::: {.flushleft data-latex=""}
**Information Box 1.** **BCP and blue carbon**
:::

@@

Estimates of global carbon export range between 5 and 12 Pg C year$^{-1}$ [@Laws2000-jl; @Dunne2007-mi; @Henson2011-mt; @Siegel2014-wg; @DeVries2017-wu; @Nowicki2022-no] with only 0.02-0.4 Pg C year$^{-1}$ reaching the sediment [@Dunne2007-mi; @Hayes2021-gg; @Nowicki2022-no] where carbon will be sequestered for millions of years. Almost all of the exported organic carbon will therefore be remineralized and sequestered away from the atmosphere on time scales ranging from months to millennia. [@Siegel2022-wd].

@@

The most well known pump is the gravitational carbon pump (BGP). It consists in the gravitational settling (i.e. sinking) of POC[^intro-3] to the deep ocean and it is the main contributor (60-70%) of the export flux [@Boyd2019-ez; @Nowicki2022-no]. Historically, the downward POC flux was directly measured using sediment traps [@Martin1987-um; @Honjo2008-kn] and indirectly measured using thorium-234 ($^{234}Th$) deficits as a POC flux proxy [e.g. @Buesseler2006-og]. More recently, the advent of underwater cameras such as the Underwater Vision Profiler 5 (UVP5) [@Picheral2010-to] allowed the direct measurement of particle size distributions (PSD, also referred to in the literature as particle size spectra (PSS)) that could then be converted to carbon fluxes [e.g. @Guidi2008-vp].

### 2023-02-21 observingCarbonCycle.qmd
update

# Modelling and observing the BCP {#sec-modelling-observing-BCP}

## Models

## Observation tools

### Historical measurements

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few. While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

In allThe study of the BCP is a really hot topic in oceanography with new platforms (e.g. unmanned surface vehicles such as saildrones or wave gliders) and new technologies (e.g. lidar) being continuously developed in the hope of understanding all its components [@Chai2020-uq; @Claustre2021-tx].

## Specific sensors for the study of the BCP {#sec-BGC-sensors}

>>>>

# Modeling and observing the BCP {#sec-modelling-observing-BCP}

## Biogeochemical models {#sec-biogeochem-models}

The study of the BCP is of paramount importance to answer the question of how much carbon is exported and how much of the exported carbon will be sequestered. In order to achieve this goal, ocean modelers have developed different kinds of biogeochemical models to better quantify the different export pathways of the BCP.

Because measuring directly the POC export flux would be challenging, it is common to estimate the fraction of the total NPP that is exported (i.e. export efficiency) [@Henson2011-mt]. This fraction is usually referred to as the $e-ratio$ (see Information Box 2 and @fig-export-ratios).

![$e-ratio$ estimations obtained with different types of models: empirical models (a, b), food-web models (c, d) and data-assimilated models (e, f). Note that the export value computed by @Laws2011-nw (9 Pg C y$^{-1}$) was recomputed by @Siegel2022-wd (6.9 Pg C y$^{-1}$), therefore the $e-ratio$ map presented here might not be representative of the one we would have got with with the initial export value. Figure taken from @Siegel2022-wd.](image/ObservingCarbonCycle/export_ratio.jpeg){#fig-export-ratios}

::: {.blackbox data-latex=""}
::: {.flushleft data-latex=""}
**Information Box 2.** **Net primary production and export ratio**
:::

Total net primary production includes new production (NP, mainly fueled from the upwelling of nitrogen from deeper water to the EZ) and regenerated production (RP, fueled with nitrogen recycled through the food web within the EZ) [@Dugdale1967-ut]. The ratio of new production over total production is referred to as the $f-ratio$ [@Eppley1979-pj].

$$
f-ratio = \frac{NP}{NP+RP}
$$

In a steady state system, new production equals export production therefore the $f-ratio$ should be equal to the ratio of export production (EP) to total NPP, referred to as the $e-ratio$ by @Laws2000-jl.

$$
e-ratio = \frac{EP}{NPP}
$$
:::

I will hereafter briefly describe a non exhaustive list of biogeochemical models to illustrate how the export production can be estimated using the $e-ratio$.

@Henson2011-mt and @Laws2011-nw (panels a and b in @fig-export-ratios) are both empirical models. @Henson2011-mt parameterized the $e-ratio$ as a decreasing function of SST (derived from satellite observations, see @fig-bgc-models) tuned on a compilation of $^{234}Th$-derived export measurement (see @sec-historical-measurements). They estimated a carbon export of 5 Pg C y$^{-1}$. @Laws2011-nw modelled the $e-ratio$ as a decreasing linear function of SST and a power-law function of NPP whose parameters were determined using particle export estimates based on estimates of new production (nitrogen-based) and $^{234}Th$ and sediment trap export flux data compiled by @Dunne2005-an. They estimated a carbon export of 9 Pg C y$^{-1}$.

@Siegel2014-wg and @Archibald2019-dj (panels c and d in @fig-export-ratios) are both food-web models (see Information Box 3). @Siegel2014-wg used a mechanistic approach using satellite observations (NPP, PSS and phytoplankton carbon concentrations, see also @fig-bgc-models) to estimate the export of the BGP. They estimated a carbon export of 6 Pg C y$^{-1}$. @Archibald2019-dj added a new module to the model of @Siegel2014-wg in order to incorporate the diel vertical migration of zooplankton for a total export of 6.5 Pg C y$^{-1}$.

::: {.blackbox data-latex=""}
::: {.flushleft data-latex=""}
**Information Box 3.** **Food-web model**
:::

A simple food-web model is the NPZD model, which consists of four state variables: Nutrient (DIN), Phytoplankton (PHYTO), Zooplankton (ZOO) and DETRITUS. The arrows represent the flows (or interactions) between the state variables (e.g. f1 represents the DIN uptake by PHYTO, f2 represents the grazing of PHYTO by ZOO, etc.), describing the sources and sinks of a given state variable \[@Soetaert2008-er\]. Forcing functions (or external variables) are external factors (i.e. not computed by the model) imposed (i.e. forced) to the model because they drive or regulate the system. Examples of forcing functions (among many others) in ecological models are light intensity (represented here by the solar radiation), temperature or wind. Finally, a model usually contains output variables (represented here by the Chlorophyll) that allow the comparison of the model to reality @Soetaert2008-er.

::: {.center data-latex=""}
![](image/ObservingCarbonCycle/npzd_no_background.png)
:::

Figure taken from [@Soetaert2008-er].
:::

@DeVries2017-wu and @Nowicki2022-no (panels e and f in @fig-export-ratios) are both data-assimilated models. These models operate by nudging model solutions to the observed fields (e.g. satellite and/or in situ data) or by optimizing model parameters to the observed fields \[@Siegel2022-wd\]. @DeVries2017-wu combined both satellite-derived data (NPP and PSS) and in situ observations (POC fluxes, DOC concentrations and dissolved $O_{2}$ distributions) to assess the carbon export and its transfer in the mesopelagic zone using a steady state ocean circulation inverse model (OCIM, the circulation component of their model). They estimated a carbon export between 7.3 and 8.6 Pg C y$^{-1}$. @Nowicki2022-no added a two-phytoplankton/two-zooplankton food-web model with a migration zooplankton component to the model of @DeVries2017-wu in order to estimate the magnitude of each export pathway of the BCP. In all, @Nowicki2022-no estimated a carbon export of 10 Pg C y$^{-1}$.

### Model uncertainties {#sec-model-uncertainties}

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of just six biogeochemical models (see @sec-biogeochem-models), we already observe strong differences. In my opinion, it means at least two things. On the one hand, we are seeing an increase in model complexity from empirical models to data-assimilated inverse models. At the same time, we also gathered more observational data as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp) that allow us to better represent its underlying processes. On the other hand, each degree of complexity propagates more and more uncertainty (@fig-bgc-models) that we need to account for in the results.

![Top of the atmosphere (TOA) radiance is converted into remote sensing reflectance $R_{rs}(\lambda)$, which is the ratio of the solar radiation reflected from the surface of the ocean that penetrates the sea surface at a discrete wavelength $\lambda$. Using TOA and $R_{rs}(\lambda)$, primary products (yellow circles) can be derived (e.g. POC, inherent optical properties (IOP), chlorophyll (Chl) or sea surface temperature (SST). Those primary products can be used in numerical models (e.g. empirical relationships) to compute secondary products (orange and red circles) such as the phytoplankton commmunity composition (PCC), particle size spectra (PSS), phytoplankton carbon concentrations (C$_{phyto})$ and the NPP. Models (light blue circles) therefore incorporate primary and secondary products as well as ancillary data (red squares) either from satellite (e.g. SST), in situ data or model-based data (ocean circulation) to estimate carbon export and sequestration (dark blue circles). Figure taken from @Siegel2022-wd.](image/ObservingCarbonCycle/carbon_models.jpeg){#fig-bgc-models width="750" height="580"}

## Observation tools {#sec-observation-tools}

### Historical measurements {#sec-historical-measurements}

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few (see also @sec-biogeochem-models. While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

In the future, new types of platforms (e.g. unmanned surface vehicles such as saildrones or wave gliders), new sensors (see @sec-BGC-sensors) and new technologies (e.g. lidar) will be continuously deployed, improved and developed in the hope of better understanding the BCP and its components [@Chai2020-uq; @Claustre2021-tx].

## Specific sensors on autonomous platforms for the study of the BCP {#sec-BGC-sensors}

The BGC-Argo array (@sec-potential-autonomous-platforms) has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to BGC-Argo floats to help fill this gap.

décrire les 2 capteurs (pour lesquels je vais m'intéresser) et finir par le projet refine, dire que ça va étudier tel et telle zone, comme cela, ça me fait une rampe de lancement pour le chapitre sur le labrador.
